\chapter{Conclusion}

\section{summary}
\section{future work}
For me, what comes first to mind when it comes to future work is how annoying and extensive time i had to put into scraping single pdfs. Every author has a different way to structure their book with different placements for pagenumbers, chapternumbers and -names which makes it really hard to find the right way to scrape them all efficiently. But plenty and clean data is so important when it is the bases for almost everything that follows up. Therefore i would condone to create the amount of literatur and characters and even improve on the already so carefully filtered data.
There is a second part to the mentioned data filtering which also leaves room to improve on which are the human-written fandom articles from fandom.com. Since some of them are so long since they contain so much detail i had to cut them to a specific paragraph. Take whole???

More evaluation methods

Since LLMs will continue to improve and might also increase their maximum input size to a point where maybe the input size will easily handle any single book, the task might shift to 

\section{note of thanks}
I would like to extend my heartfelt gratitude to all those who have knowingly or unknowingly supported me throughout the completion of this master's thesis.

First and foremost, to my advisor, Hans Ole Hatzel, for his unwavering guidance, invaluable insights, and constant encouragement. Your expertise and patience have been instrumental in shaping this research.

I would also like to thank my family and friends, whose love, support, and understanding throughout this semester provided me with both motivation and inspiration.


Finally, I am grateful to all those, named and unnamed, who have directly or indirectly contributed to this thesis. Your support has been invaluable, and I am deeply thankful for your contributions.
