\chapter{Evaluation}
As we can see the generated result doesn't contain any wrong information but is also missing a lot of details. This might be due to already mentioned missing context as well as to gpt discarding seemingly irrelevant information.
His old friends Remus Lupin and Sirius Black aren't mentioned at all and there is no info about what Sirius had to go through in consequence of Pettigrew accusing Sirius for the murder.
Although I asked gpt to only create a summary based on the given sentences, "Hermione" is mentioned in the summary which is the english name of the character Hermine. So GPT isn't fully depending on the sentences I provided for this characterization.
I utilized both the BLUE-Metric and BERT-Score to assess disparities, employing the well-known character Peter Pettigrew and the less familiar character Bathilda Bagshot and Angelina Johnson. For all three of these characters i generated characterizations. One with and one without textpassages from the book. The initial set of results, depicted in the first figure, illustrates the language model's performance solely based on its training data, devoid of any text passages revealing character information. The second figure presents findings from the subsequent test, where I incorporated all book sentences containing the character's name into the GPT query.\\
The results showcased in the second figure are only marginally superior for Bathilda and Pattigrew to those relying exclusively on training data.
I anticipated Angelina's and Bathilda's score in the initial figure to be rather low, given her limited popularity, stemming from a solitary mention in the final book. However, ChatGPT demonstrated a more profound understanding of the books than I had initially assumed.
It is crucial to conduct further assessments with books beyond the language model's training set. This can be achieved by using recently published books to validate the impact and independence of additional information on the model's performance.
\cite{post-2018-call,bert-score}
